---
Name: "Andy Gao"
title: "Stat 380 Hw 1"
format: html
editor: visual
---

## Question 2

### Consider the following vector

```{r}
my_vec <- c(
    "+0.07",
    "-0.07",
    "+0.25",
    "-0.84",
    "+0.32",
    "-0.24",
    "-0.97",
    "-0.36",
    "+1.76",
    "-0.36"
)
```

### 1. What data type does the vector contain?

Floats

### 2. Create two new vectors called my_vec_double and my_vec_int which converts my_vec to Double & Integer types, respectively,

```{r}
my_vec_double <- as.double(my_vec)
my_vec_double
```

```{r}
my_vec_int <- as.integer(my_vec)
my_vec_int
```

### 3. Create a new vector `my_vec_bool` which comprises of:

-   `TRUE`if an element in `my_vec_double` is ≤0

-   `FALSE` if an element in `my_vec_double` is ≥0

How many elements of `my_vec_double` are greater than zero?

```{r}
i = 0
my_vec_bool <- my_vec_double < i
my_vec_bool
```

### 4. Sort the values of my_vec_double in ascending order.

library(dplyr)

```{r}
sort(my_vec_double)
```

## Question 3

### 1. Provide R code to construct the following matrices


